{\fontfamily{ptm}\selectfont Extending the Convergence Results of Nesterov's Acceleration using the Proximal Gradient Gap}

### 2025-09-18 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, a lot of changes

    The lemma is crucially important and it gives us the an inequality on what happen between iterates $x_{k}, v_{k}$ and $v_{k - 1}, x_{k - 1}$ generated by algorithm satisfying Definition \ref{def:st-apg}. 

>>>>

    The lemma is crucially important and, it gives us the inequality on what happen between iterates $x_{k}, v_{k}$ and $v_{k - 1}, x_{k - 1}$ generated by algorithm satisfying Definition \ref{def:st-apg}. 
